% !TEX root = progress-llncs.tex
\section{The Unit-B Method}
\label{sec:contribution}
\newBmch[Mch]{M}
\newBevt[evt]{e}
%\newBcst[initpred]{i}

This section presents our contribution: the \unitb method which is
inspired by \eventB and \unity.
% methodology
Similar to \eventB, \unitb is aimed at the design of software systems
by stepwise refinement.  It differs from \eventB by the capability of
reasoning about progress properties and its refinement-order which
preserves liveness properties.  It also differs from \unity by
unifying the notions of programs and specifications, allowing
refinement of programs.  

\subsection{Syntax}
Similar to \eventB, in \unitb systems are modelled by a transition system,
where the state space is captured by variables $v$ and the transitions are
modelled by guarded events.  Furthermore, \unitb has additional 
assumptions on how the events should be scheduled.  Using
an \eventB-similar syntax, a \unitb event has the following form:
\begin{equation}
  \small
  \ubeventinline{\evt}{t}{\guard.t.v}{\csched.t.v}{\fsched.t.v}{\assignment.t.v.v'}~,\label{eq:ubevent}
\end{equation}
where $t$ are the parameters, $\guard$ is the \emph{guard}, $\csched$
is the \emph{coarse-schedule}, $\fsched$ is the \emph{fine-schedule},
and $\assignment$ is the \emph{action} changing state variables $v$.
The action is usually made up of several \emph{assignments}, either
deterministic ($\bcmeq$) or non-deterministic ($\bcmsuch$).
%  We use
%the short form
% \begin{equation}
%   \small
%   \ubeventinline{evt}{}{\guard.v}{\csched.v}{\fsched.v}{\assignment.v.v'}~,\label{eq:ubevent-no-par}
% \end{equation}
% for events without parameters, and
% \begin{equation}
%   \small
%   \ubeventinline{evt}{}{}{\csched.v}{\fsched.v}{\assignment.v.v'}~,\label{eq:ubevent-no-grd}
% \end{equation}
% for events without parameters and guard (the guard is $\one$).
An event $\evt$ with parameters $t$ stands for multiple events.
Each corresponds to several non-parameterised events $\evt.t$, one for
each possible value of the parameter $t$.  An event is said to be
enabled when the guard $\guard$ holds.  The scheduling assumption of
the event is represented by $\csched$ and $\fsched$ as follows: if
$\csched$ holds for infinitely long and $\fsched$ holds infinitely
often then the event is carried out infinitely often.  An event
without any scheduling assumption will have its coarse-schedule
$\csched$ equal to $\cfalse$.  An event having only the
coarse-schedule $\csched$ will have the fine-schedule to be $\one$.
Vice versa, an event having only the fine-schedule $\fsched$ will
have the coarse-schedule to be $\one$.%
% \todo{Son: (to Simon) Please make sure this convention makes sense. It
% is different from your thesis.}%
% \todo{Simon: (to Son) On page 69 of my thesis, after equation (3.7), we
% see the exact mapping that you showed above}%

In addition to the variables and the events, a model has an
initialisation state predicate \init constraining the initial value of
the state variables.
%A special event containing only action is used as the initialisation
%of the model.  
All computations of a model start from a state satisfying the
initialisation and are such that, at every step, either one of its
enabled events occurs or the state is unchanged, and each computation
satisfies the scheduling assumptions of all events.
%\todo{
% Simon: (to Son) On terminology. Above, in the section ``then'', 
% you call the part assignment and here, you call it action. My suggestion
% would be to call each of the individual clauses like $x' = x + y$ ``assignments''
% and call their conjunction ``actions''. 
% Second point: the initialization should 
% simply be a satisfiable state predicate. If we make it into an event, we're 
% stripping it of everything but the state predicate which we encode as a
% peculiar binary relation $R$ over states: one where $\qforall{x,y}{}{x(R)z \eqv y(R)z}$  }%

Properties of \unitb models are captured by two types of properties:
\emph{safety} and \emph{progress} (liveness).

\subsection{Semantics} We are going to use computation calculus to
give the semantics of \unitb models.  Let $\Mch$ be a \unitb model
containing a set of events of the form~\eqref{eq:ubevent} and an
initialisation predicate $\init$.  
%The initialisation $\init$ characterizes the set
%of initial states, corresponds a state predicate $\initpred$.
Since the action of the event can be described by a before-after
predicate $\assignment.t.v.v'$, it corresponds to an atomic action
$\Action.t ~=~ \qforall{e}{}{\initially (e = v) ~\limp~ \X \, ;
  \assignment.t.e.v}$%
%\footnote{%
%  Son: We can define this as $\qforall{e}{}{\initially (e = v) \limp
%    \X;S(t,e,v)}$%
%}%
.  Given that an event $\evt.t$ can only be carried out when it is
enabled, the effect of each event execution can therefore be
formulated as follows: $\action.(\evt.t) = \guard.t\,;\,\Action.t$.
% \todo{Son: (to Simon) I changed $\guard$ to $\guard.t$}
% \todo{Simon: (to Son) Good, I adjusted the spacing to make clearer that $.$ binds tighter than $;$}
A special constant $\SKIP$ is used to denote the atomic action that
does not change the state.
\begin{Definition}[Constant $\SKIP$]
  $\SKIP.\tau  \Wide{\eqv}  \size \tau \!=\! 2 \wide\land \tau.0\! =\! \tau.1$,
  for all traces $\tau$ ($\tau.0$, $\tau.1$ denotes the first two
  elements of $\tau$).
\end{Definition}

% \todo{Son: (to Simon) I would like to use $=$ instead of $\ew{\eqv}$}
% \todo{Simon: (to Son) That can work. You have to be careful with $=$ 
% when you open and close $\ew{ } $ many times in a formula. My advice
% would be (0) to explicitly state that $=$ and $\ew{\eqv}$ are equivalent 
% notations and (1) to use $=$ only in the case where the $\ew{ \_ }$ would
% include all the formula at hand.}

The semantics of \Mch is given by a computation predicate $\execution.\Mch$
which is a conjunction of a ``safety part'' $\safety.\Mch$ and a
``liveness part'' $\liveness.\Mch$, i.e., 
\begin{equation}
  \ew{\execution.\Mch \Wide{\eqv} \safety.\Mch \land \liveness.\Mch}~.\label{eq:execution}
\end{equation}
A property represented by a formula $s$ is satisfied by \Mch, if
\begin{equation}
  \ew{\execution.\Mch \limp s}~.\label{eq:property}
\end{equation}

\subsubsection{Safety} Below, we define the general form of one step
of execution of model \Mch and the \emph{safety} constraints on its
complete computations.
%A step of model \Mch is captured by the following
%atomic action:
\begin{align}
  \ew{\step.\Mch  \Wide{&\eqv} \qexists{\evt, t}{\evt.t \in \Mch}{\action.(\evt.t)} \,\lor\, \SKIP} \label{eq:step} \\
%\end{equation}
%Together with the initialisation, $\safety.\Mch$ is defined as follows:
%\begin{equation}
  \ew{\safety.\Mch  \Wide{&\eqv}  \initially \init \land
    \G(\step.\Mch \, ; \,\ctrue)}
\end{align}
% \todo{Simon: (to Son) I would rather not differentiate between $\initpred$ and
% $\init$. I would also prefer to use the name $\init$ everywhere. $i$ seems more
% suitable as a bound variable.}
% 

Safety properties of the model are captured by \emph{invariance} properties
(also called \emph{invariants}) and by \emph{unless} properties. 

An invariant $I(v)$ is a state-properties that hold at every reachable state of the model.
In order to prove that $I(v)$ is an invariant of $\Mch$,
we prove that $\ew{\execution.\Mch \wide{\limp} \G \initially \! I}$.
In particular, we rely solely on the safety part of the model to prove
invariance properties, i.e., we prove $\ew{\safety.\Mch \wide{\limp} \G
  \initially \! I}$.  This leads to the well-known invariance principle.
\begin{equation}
  \begin{array}{ll}
    & \ew{\init \limp I} \wide{\land} 
    \ew{\qforall{\evt, t}{\evt.t \in \Mch}{I \, ;  \action.(\evt.t) ~\limp~ \X;I}} \\
    \implies &\\
    & \ew{\safety.\Mch \limp \G \initially \! I}
  \end{array}
  \tag{INV}
\end{equation}
Invariance properties are important for reasoning about the correctness
of the models since they limit the set of reachable states.  In
particular, invariance properties can be used as additional
assumptions in proofs for progress properties.

The other important class of safety properties is defined by the
\emph{unless} operator $\un$.
\begin{Definition}[$\un$ operator]  For all state predicates $p$ and
  $q$,
  \begin{equation}
    \label{eq:un-def}
    \ew{(p \un q) \WIDE{\eqv} \G (\initially p \wide\limp (\G \initially \! p)\,;(\one \lor \X)\,;\initially q)}
  \end{equation}
\end{Definition}
Informally, $p \un q$ is a safety property stating that if condition
$p$ holds then it will hold continuously until $q$ becomes true.
The formula $(\one \lor \X)$ is used in \eqref{eq:un-def} to allow
the last state where $p$ holds and the state where $q$ first holds to 
either be the same state or to immediately follow one another.
% \todo{Son: (to Simon) Is this explanation about $\un$ clear?}
% \todo{Simon: (to Son) Is this clearer?}
The following theorem is used for proving that a \unitb model
satisfies an unless property.
\begin{Theorem}[Proving an $\un$-property]
  \label{thm:unless}
  Consider a machine \Mch and property $p \un q$.  If
  \begin{equation}
    \label{eq:un-rule}
    \qforall{\evt,t}{\evt.t \in \Mch}{\, \G \!(\,(p \, \land \! \spneg q) ; \!
      \action.(\evt.t);\!\ctrue ~\,\limp\,~ \X ; \! (p \lor q);\! \ctrue \,)}
  \end{equation}
% \todo{Simon: (to Son) be careful, $;$ binds tighter than the 
% 	logical connectives so $s\,; (t \land u)$ and $s\, ; t \,\land\, u$
% 	are vastly different}
  then $\ew{\execution.\Mch \wide\limp p \un q}$
\end{Theorem}
\begin{proof}[Sketch]
  Condition \eqref{eq:un-rule} ensures that every event of \Mch either
  maintains $p$ or establishes $q$. By induction, we can see that the
  only way for $p$ to become false after a state where it was true is
  that either $q$ becomes true or that it was already true.
\end{proof}

\subsubsection{Liveness}
For each event of the form~\eqref{eq:ubevent}, its schedule
$\schedule.(\evt.t)$ is formulated as follows, where $\csched$ and
$\fsched$ are the event's coarse- and fine-schedule, respectively.
\begin{equation}
  \label{eq:schedule}
  \ew{\schedule.(\evt.t) \WIDE{\eqv} \G (\G \initially \!\csched
      \,\land\, \G \F\,;\initially \fsched  \wide{\limp} 
      \F\,;\fsched\,;\action.(\evt.t)\,;\ctrue)}~.
\end{equation}
To ensure that the event $\evt.t$ only occurs when it is enabled, we
require the following \emph{feasibility} condition:
\begin{equation}
  \label{eq:fis}
  \ew{\execution.\Mch \Wide{\limp} \G \initially \!(c \land f \, \limp\, g)}
  \tag{SCH-FIS}
\end{equation}

Our scheduling is a generalisation of the standard weak-fairness and
strong-fairness assumptions. The standard \emph{weak-fairness}
assumption for event $\evt$ (stating that if the event is enabled
infinitely long then eventually it will be taken) can be formulated
by using $\csched = \guard$ and $\fsched = \one$.
Similarly, the standard \emph{strong-fairness} assumption for $\evt$
(stating that if the event is enabled infinitely often then eventually
it will be taken) can be formulated by using $\csched = \one$ and
$\fsched = \guard$.
\begin{equation}
  \ew{ \wf.(\evt.t)  \2\equiv  \G (\G \bullet \guard \1\implies \F;\action.(\evt.t);\ctrue) }
\end{equation}
\begin{equation}
  \ew{ \strf.(\evt.t)  \2\equiv  \G (\G \F;\bullet \guard \1\implies \F;\action.(\evt.t);\ctrue) }
\end{equation}



The liveness part of the model is the conjunction of the schedules for its
events, i.e.,
\begin{equation}
  \label{eq:liveness}
  \ew{\liveness.\Mch \Wide{\eqv} \qforall{\evt, t}{\evt.t \in \Mch}{\schedule.(\evt.t)}}~
\end{equation}

% semantics
% We will now discuss the semantics of the temporal logic we will be
% using, the semantics of our notion of program and the definition of
% refinement together with some rules.  All the semantics is expressed
% using computation calculus \cite{Dijkstra:1998p1128}.  For the sake of
% brevity, the proofs of the various properties of the semantics are
% omitted but they can be found in \cite{thesis/hudon2011}.

\subsection{Progress Properties}
\label{sec:progress-properties}
Progress properties are of the form $p \leadsto q$, where
$\leadsto$ is the leads-to operator and is defined as follows.
\begin{Definition}[$\leadsto$ operator] For all state predicates $p$
  and $q$,
  \begin{equation}
    \label{eq:leadsto}
    \ew{(p \leadsto q) \WIDE{\eqv} \G (\initially p \wide{\limp} \F \initially \! q) }
  \end{equation}
\end{Definition}
In this paper, properties and theorems are often written without
explicit quantifications: these are universally quantified over all
values of the free variables occurring in them.

Important properties of $\leadsto$ are as follows. For state
predicates $p$, $q$, and $r$, we have:
%\begin{equation}
%  \label{eq:leadsto-one}
%  \ew{ p \leadsto \one}
%\end{equation}
% \todo{Simon: (to Son) Do you really need $p \leadsto \one$? We could
%   put disjunction instead}
\begin{align}
%  \label{eq:disjunction}
%  \ew{ \qexists{i}{}{p.i} \leadsto q \WIDE{&\eqv} \qforall{i}{}{p.i \leadsto q}
%  }\tag{Disjunction} \\
%  \label{eq:lhs-antimon}
%  \ew{ \G \initially\!(p \limp q) \WIDE{\limp} (\,(q \leadsto r) \wide{& \limp} (p \leadsto r)\,) }
%  \tag{LHS-Antimonotonicity}\\
  \ew{ (p \limp q) \WIDE{&\limp} (p \leadsto q)
  }\tag{Implication}\label{eq:implication} \\
  \ew{ (p \leadsto q) \land (q \leadsto r) \WIDE{&\limp} (p \leadsto r)
  }\tag{Transitivity}\label{eq:transitivity}
  \\
  \label{eq:37} 
  \ew{ (p \leadsto q)  \WIDE{&\eqv}  (p \,\land \! \spneg q \Wide{\leadsto} q)
  }\tag{Split-Off-Skip}
\end{align}
% \todo{Son: (to Simon) Think about the name for
%   \eqref{eq:37}}

The main tool for reasoning about progress properties in \unitb is the \emph{transient operator} $\tr$. 
\begin{Definition}[$\tr$ operator] For all state predicate $p$, $\ew{\tr p \Wide{\eqv} \G \F \, ;\initially\! \spneg p}$.
%  \begin{equation}
%    \ew{\tr p \Wide{\eqv} \G \F \, ;\initially\! \spneg p}~.\label{eq:transient}
%  \end{equation}
\end{Definition}
$\tr p$ states that state predicate $p$ is infinitely often false.
The relationship between $\tr$ and $\leadsto$
is as follows:
\begin{equation}
  p \wide{\leadsto} \spneg p  \WIDE{=} \one \wide{\leadsto} \spneg p \WIDE{=}
  \tr p~.
  \label{eq:trans-prop}
\end{equation}

The attractiveness of properties such as $\tr p$ is that we can
\emph{implement} these using a single event as follows.
\begin{Theorem}[Implementing $\tr$]
  \label{thm:transient} Consider a \unitb model \Mch and a transient
  property $\tr p$. We have
  $\ew{\execution.\Mch \limp \tr p}$, if there exists an event 
  \[\ubeventinline{\evt}{t}{\guard.t.v}{\csched.t.v}{\fsched.t.v}{\assignment.t.v.v'}~.\]
  that is to say $\execution.\Mch$ entails:
  \begin{equation}
  	\label{eq:LIVE}
  	\G (\G \initially \!c \land \G \F\,;\initially f \wide{\limp} \F\,; f\, ; \action.(\evt.t) ) ~ ,
  	\tag{LIVE}
  \end{equation}
  and parameter $t$ such that $\evt.t \in \Mch$ and $\execution.\Mch$ entails each of the conditions below:
  \begin{equation}
    \G \initially\!(p \limp \csched)~,\label{eq:SCH}
    \tag{SCH}
  \end{equation}
  \begin{equation}
    \csched \leadsto \fsched~,\label{eq:OP}
    \tag{PRG}
  \end{equation}
  \begin{equation}
    \G (~ (p \land \csched \land \fsched)\,; \action.(\evt.t) \, ; \ctrue \wide{\wide\limp} \X\,; \initially \! \spneg p~)~.
    \tag{NEG}
    \label{eq:NEG}
  \end{equation}
\end{Theorem}
\begin{proof}
  In this case, $\G$ acts as an everywhere operator which allows us to
  prove $\F;\initially \spneg p$ instead of $\G \F;\! \initially \!
  \spneg p$.  Additionally, since $\ew{ \neg s \limp s \wide{\eqv} s
  }$ for any computation predicate $s$, we discharge our proof
  obligation by strengthening $\F\; ; \, \initially \! \spneg p$ to
  its negation, $\G \initially \! p$.
    \begin{calculation}
    	\F \, ; \initially\! \spneg p
    \hint{\follows}{ $\ew{ \F\,;\X \limp \F}$, aiming for \eqref{eq:NEG} }
    	\F \, ; \X \, ; \initially \! \spneg p
    \hint{\follows}{ \eqref{eq:NEG} }
    	\F\, ; (p \land c \land f) \, ; \action \, ; \ctrue
    \hint{\follows}{ computation calculus }
%    	\F\, ; (~(c \land f) ; \! \action ; \! \ctrue \wide{\land} \initially \!\!\, p~)
%    \hint{\follows}{ $\G$ is strengthening then persistence rule }
	\F ;\! f ; \! \action ; \! \ctrue \wide{\land} \G \initially \! c \wide{\land} \G \initially \! p
    \hint{\follows}{ \eqref{eq:LIVE}; $\G$ is conjunctive }
    	\G  \F ; \! \initially f \wide{\land} \G \initially\! c \wide{\land} \G \initially \! p
    \hint{=}{ \eqref{eq:OP} }
    	\G \initially \! c \wide{\land} \G \initially \! p
    \hint{=}{ $\G$ is conjunctive; \eqref{eq:SCH} }
    	\G \initially \! p
    \end{calculation}
%  We prove $\tr p$ under the assumption $\execution.\Mch$.
%
%  First, we prove that $\G \initially p \limp \G \initially \csched$
%  as follows.
%  \begin{Reason}
%    \Step{}{\execution.\Mch}
%    \StepR{$\limp$}{~\eqref{eq:SCH}}{
%      \G \initially(p \limp \csched)
%    }
%    \StepR{$\limp$}{$\G$ is monotonic \eqref{eq:g-monotonic}}{
%      (\G \initially p \limp \G \initially \csched)
%    } 
%  \end{Reason}
%  
%  Second, we prove
%  that $ (\G \initially \csched \limp \G \F;\initially \fsched)$ as
%  follows.
%  \begin{Reason}
%    \Step{}{\execution.\Mch}
%    \StepR{$\limp$}{\eqref{eq:OP}}{
%      \csched \leadsto \fsched
%    }
%    \StepR{=}{Definition \eqref{eq:leadsto}}{
%      \G (\initially \csched \limp \F;\initially \fsched)
%    }
%    \StepR{$\limp$}{$\G$ is strengthening}{
%      (\initially \csched \limp \F;\initially \fsched)
%    }
%    \StepR{$\limp$}{$\G$ is monotonic}{
%      (\G \initially \csched \limp \G \F;\initially \fsched)
%    }
%  \end{Reason}
%  Furthermore, we have $\G (\G \initially p \wide{\limp} \G
%      \F\,;(p \land \csched \land \fsched)\,;\action.(\evt.t)\,;\ctrue)$ according to the following
%      reasoning.
%  \begin{Reason}
%    \Step{}{\execution.\Mch}
%    \StepR{$\limp$}{Definition \eqref{eq:execution}}{\liveness.\Mch}
%    \StepR{$\limp$}{Definition
%      \eqref{eq:liveness}}{\schedule.(\evt.t)}
%    \StepR{$=$}{Definition \eqref{eq:schedule}}{
%      \G (\G \initially \csched
%      \land \G \F;\initially \fsched  \wide{\limp} \G
%      \F;\fsched;\action.(\evt.t);\ctrue)      
%    }
%    \StepR{$=$}{$\G \initially \csched \limp \G \F;\initially \fsched$}{
%      \G (\G \initially \csched \wide{\limp} \G
%      \F;\fsched;\action.(\evt.t);\ctrue)      
%    }
%    \StepR{$=$}{$\G \initially \csched$}{
%      \G (\G \initially \csched \wide{\limp} \G
%      \F;\csched \land \fsched;\action.(\evt.t);\ctrue)      
%    }
%    \StepR{$\limp$}{$\G \initially p \limp \G \initially \csched$}{
%      \G (\G \initially p \wide{\limp} \G
%      \F;\fsched;\action.(\evt.t);\ctrue)      
%    }
%    \StepR{$\limp$}{$\G \initially p$}{
%      \G (\G \initially p \wide{\limp} \G
%      \F;p \land \csched \land \fsched;\action.(\evt.t);\ctrue)      
%    }
%    \StepR{$\limp$}{~\eqref{eq:NEG}}{
%      \G (\G \initially p \wide{\limp} \G
%      \F;\X;\spneg p;\ctrue)
%    }
%    \StepR{$\limp$}{$\F;\X \limp \F$}{
%      \G (\G \initially p \wide{\limp} \G
%      \F;\spneg p;\ctrue)
%    }
%  \end{Reason}
%
%  Finally, we have
%  \begin{Reason}
%    \Step{}{(\G (\G \initially p \wide{\limp}  \G
%      \F;\spneg p;\ctrue) \Wide{\limp} \tr p)}
%    \StepR{=}{Definition of $\tr$ \eqref{eq:transient}}{
%      (\G (\G \initially p \wide{\limp}  \G
%      \F;\spneg p;\ctrue) \Wide{\limp} \G \F;\spneg p;
%      \true)
%    }
%    \StepR{$\follows$}{$\G$ is monotonic}{
%      ((\G \initially p \wide{\limp}  \G
%      \F;\spneg p;\ctrue) \Wide{\limp} \F;\spneg p; \true)
%    }
%    \WideStepR{=}{$\G \initially p  = \neg (\F;\spneg p; \true)$}{
%      ((\G \initially p \wide{\land}  \G
%      \F;\spneg p;\ctrue) \land \G \initially p \Wide{\limp} \F;\spneg p; \true)
%    }
%    \StepR{$\follows$}{Predicate logic}{
%      (\G \F;\spneg p;\ctrue \Wide{\limp} \F;\spneg p; \ctrue)
%    }
%    \StepR{=}{$\G$ is strengthening \eqref{eq:g-strengthen}}{
%      \ctrue
%    }
%  \end{Reason}
\end{proof}
(Due to space restriction, for the rest of this paper, we only present
sketch proofs of theorems. Detailed proofs are available
in~\cite{thesis/hudon2011}).

Condition \eqref{eq:SCH} is an invariance property. Condition
\eqref{eq:OP} is a progress property.  Condition \eqref{eq:NEG} states
that event $\evt.t$ establish $\spneg p$ in one step.  In practice,
often we design $\csched$ such that it is the same as $p$ and
$\fsched$ is $\one$ (i.e., omitting $\fsched$); as a result,
conditions \eqref{eq:SCH} and \eqref{eq:OP} are trivial.  Condition
\eqref{eq:NEG} can take into account any invariance property $I$ and
can be stated as $\ew{I \land p \land \csched \land \fsched;
  \action.(\evt.t) \limp \X; \spneg p}$.

In general, progress properties can be proved using the following
\emph{ensure-rule}.  The rule relies on proving an unless property and
a transient property.
\begin{Theorem}[The ensure-rule] For all state predicates $p$ and $q$,
  \label{thm:ensure-rule}
  \begin{equation}
    \label{eq:ensure-rule}
    \ew{(p \un q) \land (\tr p \land \spneg q)  \WIDE\limp (p \leadsto q)}
  \end{equation}
\end{Theorem}
\begin{proof}[Sketch]
  $p \un q$ ensures that if $p$ holds then it will hold for infinitely long or
  eventually $q$ holds.  If $q$ holds eventually then we have $p
  \leadsto q$.  Otherwise, if $p$ holds for infinitely long and $\spneg q$
  also hold for infinitely long, we have a contradiction, since $\tr p \land
  \spneg q$ ensures that eventually $p \land \spneg q$ will be
  falsified.  As a result, if $p$ holds for infinitely long then eventually
  $q$ has to hold.
\end{proof}

\subsection{Refinement}
\label{sec:refinement}
\newBmch[cncMch]{N}

In this section, we develop rules for refining \unitb models such that
safety and liveness properties are preserved.  Consider a machine \Mch
and a machine \cncMch, \cncMch refines \Mch if
\begin{equation}
  \label{eq:ref}
  \ew{\execution.\cncMch \limp \execution.\Mch}~.
  \tag{REF}
\end{equation}
As a result of this definition, any property of \Mch is also satisfied
by \cncMch.  Similarly to \eventB, refinement is considered in \unitb
on a per event basis.  Consider an abstract event $\evt.t$ belong to
\Mch and a concrete event $\cncevt.t$ belong to \cncMch as follows.
\begin{equation}
  \ubeventinline{\evt}{t}{\guard.t.v}{\csched.t.v}{\fsched.t.v}{\assignment.t.v}\label{eq:absevt}
\end{equation}
\begin{equation}
  \ubeventinline{\cncevt}{t}{\cncguard.t.v}{\cnccsched.t.v}{\cncfsched.t.v}{\cncassignment.t.v}~.\label{eq:cncevt}
\end{equation}
We have $\cncevt.t$ is a refinement of $\evt.t$ if
\begin{equation}
  \label{eq:evt-safety}
  \ew{\execution.\cncMch \limp (\action.(f.t) \limp \action.(e.t))}~, \textrm{and}
  \tag{EVT-SAF}
\end{equation}
\begin{equation}
  \label{eq:evt-live}
  \ew{\execution.\cncMch \limp (\schedule.(f.t) \limp \schedule.(e.t))}
  \tag{EVT-LIVE}
\end{equation}
A similar rule is presented for the initialisation.  The proof that
\cncMch refines \Mch (i.e., \eqref{eq:ref}) given conditions such as
\eqref{eq:evt-safety} and \eqref{eq:evt-live} is left out.  A special
case of event refinement is when the concrete event \cncevt is a new
event.  In this case, \cncevt is proved to be a refinement of a special
\SKIP{} event which is unscheduled and does not change any variables.

Condition \eqref{eq:evt-safety} leads to similar proof obligations in
\eventB such as \emph{guard strengthening} and \emph{simulation}.  We
focus here on expanding the condition \eqref{eq:evt-live}.  The
subsequent theorems are related to concrete event
\cncevt~\eqref{eq:cncevt} and abstract event \evt~\eqref{eq:absevt},
under the assumption that condition \eqref{eq:evt-safety} has been
proved.  They illustrate different ways of refining event scheduling
information: \emph{weakening the coarse-schedule}, \emph{replacing the
  coarse-schedule}, \emph{strengthening the fine-schedule}, and
\emph{removing the fine-schedule}.

\begin{Theorem}[Weakening the coarse-schedule]
  Given $\cncfsched = \fsched$. If
  \begin{center}
    $\ew{\execution.\cncMch \WIDE\limp \G \initially(\csched \limp
      \cnccsched)}$ \WIDE{then} $\ew{\execution.\cncMch \limp
      (\schedule.(\cncevt.t) \limp \schedule.(\evt.t))}$~.
  \end{center}

\end{Theorem}
\begin{proof}[Sketch]
  The coarse-schedule is at an anti-monotonic position within the definition of
  $\schedule$.
\end{proof}

\begin{Theorem}[Replacing the coarse-schedule]
  \label{thm:ref-rep-crs}
  Given $\cncfsched = \fsched$.  If
  \begin{equation}
    \ew{\execution.\cncMch \WIDE{\limp} \csched 
         \wide\leadsto \cnccsched}\label{eq:crs}
  \end{equation}
  \begin{equation}
    \label{eq:unless}
    \ew{\execution.\cncMch \WIDE{\limp} \cnccsched ~\un~ \spneg \csched}~,
  \end{equation}
  then $\ew{\execution.\cncMch \limp (\schedule.(\cncevt.t) \limp \schedule.(\evt.t))}$
\end{Theorem}
\begin{proof}[Sketch]
  Conditions~\eqref{eq:crs} and~\eqref{eq:unless} ensures that if $\csched$ holds
  then eventually $\cnccsched$ holds and it will hold for at least as long as $\csched$
  As a result, if
  $\csched$ holds for infinitely long, $\cnccsched$ also holds for infinitely long.  Hence
  the schedule for \cncevt is stronger than that of \evt.
\end{proof}

\begin{Theorem}[Strengthening the fine-schedule]
  \label{thm:strengthen-fns}
  Given $\cnccsched = \csched$. If
  \begin{equation}
    \label{eq:fns}
    \ew{\execution.\cncMch \WIDE{\limp} \G \initially(\cncfsched \limp
      \fsched)}~, \textrm{and}
  \end{equation}
  \begin{equation}
    \label{eq:lts}
    \ew{\execution.\cncMch \WIDE{\limp} \fsched \wide\leadsto \cncfsched}
  \end{equation}
  then $\ew{\execution.\cncMch \limp (\schedule.(\cncevt.t) \limp \schedule.(\evt.t))}$.
\end{Theorem}
\begin{proof}[Sketch] We can prove  
  $\schedule.(\evt.t)$ under the assumptions 
  $\schedule.(\cncevt.t)$ and $\execution.\cncMch$ 
  by calculating from $\F \, ; (\csched \land \fsched) \, ; \action.(\evt.t)\, ; \ctrue$ 
  (the right hand side of $\schedule.(\evt.t)$) and applying 
  one assumption after the other (in this order \eqref{eq:fns}, 
  \eqref{eq:evt-safety}, $\schedule.(\cncevt.t)$, \eqref{eq:lts}) 
  to strengthen it to $\G \initially\! c \land \G \F\,;\initially\!f$ 
  (the right hand side of $\schedule.(\evt.t)$).
%     \begin{equation}
%       \schedule.(\cncevt.t) \label{eq:sfs:cfs}
%     \end{equation}
%   and $\execution.\cncMch$
%     \begin{calculation}
%     	\F\,;(\csched\land \fsched)\,;\action.\evt \, ; \ctrue
%     \hint{\follows}{ \eqref{eq:fns} }
%     	\F\,;(\csched\land \cncfsched)\,;\action.\evt \, ; \ctrue
%     \hint{\follows}{ \eqref{eq:evt-safety} }
%     	\F\,;(\csched\land \cncfsched)\,;\action.\cncevt \, ; \ctrue
%     \hint{\follows}{ \eqref{eq:sfs:cfs} and $\ew{ \F \eqv \F\,\F}$ }
%     	\G \initially\! \csched \land \G \F ; \! \F  ; \! \initially \cncfsched
%     \hint{\follows}{ \eqref{eq:lts} }
%     	\G \initially\! \csched \land \G  \F  ; \! \initially \fsched
%     \end{calculation}
% 
%%%Other proof
%  \begin{Reason}
%    \Step{}{\schedule.(\cncevt.t)}
%    \StepR{$=$}{Definition (\ref{eq:schedule})}{
%      \G (\G \initially \cnccsched \land \G \F;\initially
%      \cncfsched \limp \G\F;\cncfsched;\action.(\cncevt.t);\ctrue)
%    }
%    \StepR{=}{\eqref{eq:lts}}{
%      \G (\G \initially \cnccsched \limp \G\F;\cncfsched;\action.(\cncevt.t);\ctrue)
%    }
%    \StepR{$\limp$}{\eqref{eq:fns}}{
%      \G (\G \initially \cnccsched \limp \G\F;\fsched;\action.(\cncevt.t);\ctrue)
%    }
%    \StepR{$\limp$}{assumption $\action.(f.t) \limp \action.(e.t)$}{
%      \G (\G \initially \cnccsched \limp \G\F;\fsched;\action.(\evt.t);\ctrue)
%    }
%    \StepR{$\limp$}{$\cnccsched = \csched$}{
%      \G (\G \initially \csched \limp \G\F;\fsched;\action.(\evt.t);\ctrue)
%    }
%    \StepR{$\limp$}{Predicate logic}{
%      \G (\G \initially \csched \land \G \F;\fsched \limp \G\F;\fsched;\action.(\evt.t);\ctrue)
%    }
%    \StepR{$=$}{Definition (\ref{eq:schedule})}{
%      \schedule.(\evt.t)
%    }
%  \end{Reason}
\end{proof}

\begin{Theorem}[Removing the fine-schedule]
\label{thm:remove-fns}
  Given $\cnccsched = \csched$ and $\cncfsched = \one$. If
  \begin{equation}
    \label{eq:remove-fns}
    \ew{\execution.\Mch \WIDE\limp \G \initially (\csched \limp \fsched)}
  \end{equation}
  then $\ew{\execution.\cncMch \limp (\schedule.(\cncevt.t) \limp \schedule.(\evt.t))}$.
\end{Theorem}
\begin{proof}[Sketch]
  Condition \eqref{eq:remove-fns} ensures that when $\csched$ holds
  for infinitely long, $\fsched$ holds for infinitely long, hence we can remove the
  fine-schedule $\fsched$, i.e., replaced it by $\one$.
\end{proof}
%\input{temp-prop}

%\input{semantics}

%\input{refinement}

%\input{method}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "progress"
%%% End: 
