\section{Conclusion}
\label{sec:conclusion}

We presented in this paper \unitb, a formal method inspired by \eventB
and \unity.  Our method allows systems to be developed gradually via
refinement and support reasoning about both safety and liveness
properties.  An important feature of \unitb is the notion of coarse-
and fine-schedules for events.  Standard weak- and strong-fairness
assumptions can be expressed using these event schedules.  We
proposed refinement rules to manipulate the coarse-
and fine-schedules such that liveness properties are
preserved.  We illustrated \unitb by developing a signal control
system.

A key observation in \unitb is the role of event scheduling regarding
liveness properties being similar to the role of guards regarding safety
properties.  Guards prevents events to occur in some unsafe state such
that safety properties cannot be violated.  Schedules ensure event
occurrences such that liveness properties can be satisfied.  Another
key aspect of \unitb is the role of progress properties during
refinement.  Often, to ensure the validity of a refinement, one needs
to prove some progress properties which (eventually) can be
``implemented'' (satisfied) by some scheduled events.

\paragraph{Related work}
\input{rel-work}

\paragraph{Future work}

%%%%% Data refinement
Currently, we only consider superposition refinement in \unitb where
variables are retained during refinement.  More generally, variables
can be removed and replaced by other variables during refinement (data
refinement).  We are working on extending \unitb to support data
refinement.  We expect to have more refinement rules to complement the
current set of rules.

%%%%% Decomposition/Composition 
Another important technique for coping with the difficulties in
developing complex systems is composition/decomposition and is already
a part of methods such as \eventB and \unity.  We intend to investigate
on how this technique can be added to \unitb, in particular, the role
of event scheduling during composition/decomposition.

%%%%% Tool support
Given the close relationship between \unitb and \eventB, we are
looking at extending the supporting Rodin
platform~\cite{abrial10:_rodin} of \eventB to accomodate \unitb.  We
expect to generate the corresponding proof obligations according to
different refinement rules such that it can be verified using the
existing provers of Rodin.


%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "progress"
%%% End: 
